Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-07-24 doc/bcspaper/article.tex
Updated bib style in line with BCS:SGAI guidelines

% in conclusions add how this can give recommendations for Plos and other
% journals 
A script called {\em plosget.py} was written, in order to download the
papers via the PloS RESTful search API\footnote{\url{http://api.plos.org/solr/faq/}}. The number of papers downloaded per
paper type category was as follows: 200 Essay, 99 Correspondence, 107 Case
Study, 200 Perspective, 74 Viewpoint, 93 Opinion, 312 Review, 200 Research.
These formed a corpus of 1285 %1459-174 after removing synopsis. Should double
check the numbers add up papers.

@@

\bibliographystyle{plain}
\bibliography{partridge}

>>>>

% in conclusions add how this can give recommendations for Plos and other
% journals 
A script called {\em plosget.py}\footnote{\url{https://github.com/ravenscroftj/partridge}} was written, in order to download the
papers via the PloS RESTful search API\footnote{\url{http://api.plos.org/solr/faq/}}. The number of papers downloaded per
paper type category was as follows: 200 Essay, 99 Correspondence, 107 Case
Study, 200 Perspective, 74 Viewpoint, 93 Opinion, 312 Review, 200 Research.
These formed a corpus of 1285 %1459-174 after removing synopsis. Should double
check the numbers add up papers.

@@

\bibliographystyle{acm}
\bibliography{partridge}
